### 2017-03-29 thesis/discussion/discussion.tex
tmp commit

The predictions of the obesity metagene scores were made using the linear models created in the \gls{nzbc} data set.
All of the predicted obesity metagene scores significantly correlated with the true obesity metagene scores in both the \gls{nzbc} (training) and CR (testing) data sets.
% TODO: check r-squared values
However, the $R^2$-values for all of these predictions were low (highest $R^2$ $\approx$ 0.42; \cref{sec:summary_statistics_of_the_predicted_obesity_metagenes_with_sample_bmi_bmi_status_in_nzbc_and_cr_data}) with highly variable data points in the scatter plots.
It was unclear from these predictions and plots whether the models explained the true underlying biological mechanisms of the obesity associated genetic signatures.
Nevertheless, the models did explain some variations in the obesity metagenes, but there may be some other unknown biological processes that provide more information about the signatures.

Since linear models were created only with the ``consistent'' pathway metagene scores, a step wise method was used to generate linear models that included the patient \gls{bmi}, \gls{bmi} status and all of the pathway metagenes that allowed the model to predict the true obesity metagene the best.
% TODO: check r-squared values
As shown by the results in \cref{sec:prediction_of_obesity_associated_metagene_with_pathway_associate_metagene}, all of the models predicted the true obesity metagene scores with high $R^2$-value in Creighton's data set (highest $R^2$ $\approx$ 0.88) and were statistically significant.
This meant that the variables that were significant in the linear models played a role in the obesity associated genetic signatures.
There was no single pathway signature that was common to all of the linear models, but Akt, \gls{egfr} and Src pathway metagenes were included in many of the models, which suggested that these pathway signatures may have an important role in the obesity associated genetic signatures (\cref{sub:stepwise_linear_model_prediction_in_nzbc_and_cr_data_sets}).

@@

As shown clearly by the results from \cref{cha:obesity_genetic_signatures_and_cancer}, there seemed to be no  genetic signatures that were able to differentiate between the tumour samples from the patients that were obese from those that were not, across different cancer types.
Furthermore, there were no genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
These results have suggested that there were no obesity specific genetic signatures that were common across different cancer types.
The results from \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures} showed that the obesity associated genetic signatures generated from the Creighton \textit{et al.} data set were different from those generated from the Fuentes-Mattei \textit{et al.} data set.
None of the pathway associated genetic signatures showed positive correlation with any of the obesity associated genetic signatures in the heatmap.
However, strong negative correlation with the Akt, \gls{er}, \gls{egfr}, \gls{pr}, p53, Src and \gls{tgfb} pathways, suggesting that the possibility of the obesity associated genetic signatures were picking up the signals from these pathways, rather than the signals from the obesity phenotype of the patients.

>>>>

The predictions of the obesity metagene scores were made using the linear models created in the \gls{nzbc} data set.
All of the predicted obesity metagene scores significantly correlated with the true obesity metagene scores in both the \gls{nzbc} (training) and CR (testing) data sets.
However, the $R^2$-values for all of these predictions were low (highest $R^2$ $\approx$ 0.42; \cref{sec:summary_statistics_of_the_predicted_obesity_metagenes_with_sample_bmi_bmi_status_in_nzbc_and_cr_data}) with highly variable data points in the scatter plots.
It was unclear from these predictions and plots whether the models explained the true underlying biological mechanisms of the obesity associated genetic signatures.
Nevertheless, the models did explain some variations in the obesity metagenes, but there may be some other unknown biological processes that provide more information about the signatures.

Since linear models were created only with the ``consistent'' pathway metagene scores, a step wise method was used to generate linear models that included the patient \gls{bmi}, \gls{bmi} status and all of the pathway metagenes that allowed the model to predict the true obesity metagene the best.
As shown by the results in \cref{sec:prediction_of_obesity_associated_metagene_with_pathway_associate_metagene}, all of the models predicted the true obesity metagene scores with high $R^2$-value in the CR data set (highest $R^2$ $\approx$ 0.8869) and were statistically significant.
This meant that the variables that were significant in the linear models played a role in the obesity associated genetic signatures.
There was no single pathway signature that was common to all of the linear models, but Akt, \gls{egfr} and Src pathway metagenes were included in many of the models, which suggested that these pathway signatures may have an important role in the obesity associated genetic signatures (\cref{sub:stepwise_linear_model_prediction_in_nzbc_and_cr_data_sets}).

@@

As shown clearly by the results from \cref{cha:obesity_genetic_signatures_and_cancer}, there seemed to be no  genetic signatures that were able to differentiate between the tumour samples from the patients that were obese from those that were not, across different cancer types.
Furthermore, there were no genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
These results have suggested that there were no obesity specific genetic signatures that were common across different cancer types.
The results from \cref{cha:obesity_associated_genetic_signature_and_pathway_signatures} showed that the obesity associated genetic signatures generated from the Creighton \textit{et al.} data set were different from those generated from the Fuentes-Mattei \textit{et al.} data set.
None of the pathway associated genetic signatures showed positive correlation with any of the obesity associated genetic signatures in the heatmap.
However, strong negative correlation with the Akt, \gls{er}, \gls{egfr}, \gls{pr}, p53, Src and \gls{tgfb} pathways, suggesting that the obesity associated genetic signatures were picking up the signals from these pathways, rather than the signals from the obesity phenotype of the patients.

### 2017-03-29 thesis/intro/intro.tex
tmp commit

@@

This research aims to determine whether gene expression signatures exist  that are specific to obesity across multiple cancer types, and to investigate whether there are any common pathways being dysregulated in cancers based on these genetic signatures.
Better understanding of the pathways being dysregulated in cancer cells in obese patients may lead to improved clinical decisions, and contribute towards personalised treatment in the future.

>>>>

\vspace{-2mm}

@@

This research aims to determine whether gene expression signatures exist  that are specific to obesity across multiple cancer types, and to investigate whether there are any common pathways being dysregulated in cancers based on these genetic signatures.
A better understanding of the pathways being dysregulated in cancer cells in obese patients may lead to improved clinical decisions, and contribute towards personalised treatment in the future.

### 2017-03-29 thesis/methods/methods.tex
tmp commit

The raw \gls{rnaseq} data from the \gls{icgc} database were formatted in such a way that the count data of all the genes were listed for one sample, then the count data for all the genes for the next sample, and so on.
This data format was highly inconvenient for later analyses so the data were reformatted into a ``gene by sample'' matrix format using the \textit{dplyr} package in \gls{r}.

Another problem with the data was the sample ID in the \gls{rnaseq} data.
Though similar to the \gls{tcga} sample IDs, the \gls{icgc} IDs in the \gls{rnaseq} data had an extra identification code in the sample names.
To associate each sample in the raw \gls{rnaseq} data from the \gls{icgc} database with the correct samples in the clinical data from the \gls{tcga} database, the \gls{icgc} IDs were re-coded so they matched the \gls{tcga} IDs.
After the IDs were re-coded, all of the samples were checked to see if there were any duplicates in either the \gls{icgc} \gls{rnaseq} data or the \gls{tcga} clinical data.
Where there was a duplicate in the sample ID, a single sample with the highest mean expression value was chosen to represent that particular ID by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r} \citep{Langfelder2008}.

@@

\begin{table}[htpb]
	\caption{Summary of the sample \gls{bmi} status in the \gls{icgc} cancer data}
	\label{tab:icgc_bmi}
	\begin{center}
		\begin{tabular}{lcccc}
			& \multicolumn{4}{c}{Number of samples}\\
			\cmidrule(r){2-5}
			Cancer type & Normal weight & Overweight & Obese & Total\\
			\hline
			\hline
			\rule{0pt}{2.25ex}BLCA & 103 & 97  & 61  & 261 \\
			CESC                   & 83  & 64  & 77  & 224 \\
			COAD                   & 75  & 81  & 70  & 226 \\
			KIRP                   & 26  & 53  & 45  & 124 \\
			LIHC                   & 139 & 76  & 49  & 264 \\
			READ                   & 22  & 36  & 15  & 73  \\
			SKCM                   & 71  & 74  & 73  & 218 \\
			UCEC                   & 88  & 108 & 286 & 482 \\
			\hline
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

\gls{kegg} is a genomic database constructed by \citet{Kanehisa2000} that store information about genes, pathways and ligands for a variety of species.
The \gls{kegg} database also curates other information such as the approved drugs in US and Japan and genes related to diseases, making it a great tool for exploring the biological significance of genes and pathways \citep{Kanehisa2008}.

The \textit{KEGG.db} package was used to load the \gls{kegg} database into \gls{r} \citep{kegg}.
Only the human related \gls{kegg} terms were used in pathway enrichment analysis, and these terms were organised into a format so that the pathways were able to be queried using the gene symbol.

@@

The Reactome database is a ``curated, peer-reviewed resource of human biological processes'' \citep{Joshi2005}.
The Reactome database is constructed based on the reactions that have direct evidence from the literature, which are connected into higher order pathway structures \citep{Joshi2005}.

The \textit{reactome.db} package was used to load the Reactome database into \gls{r} \citep{reactome}.
Only the human related Reactome terms were used in pathway enrichment analysis, and these terms were organised into a format so that the pathways were able to be queried using the gene symbol.

@@

Since the \gls{nzbc} data was the only data set other than the Creighton \textit{et al.} data set that had the patient \gls{bmi} information, all of the linear models were constructed in the \gls{nzbc} data set.
Eleven linear models were created in the \gls{nzbc} to predict the obesity associated metagene from the \citet{Creighton2012} study.
First seven models created were combinations of the sample \gls{bmi}, \gls{bmi} status and a selection of pathway associated metagene scores.
The selected pathways used in the linear model construction were \gls{bcat}, \gls{er}, \gls{ifna}, \gls{ifny}, Myc and \gls{pr}.
In deciding on the pathways to be used for the construction of the linear model, the correlation of the \gls{svd}- and transformation matrix-derived pathway metagene scores in different data sets were examined.

>>>>

The raw \gls{rnaseq} data from the \gls{icgc} database were formatted so that the count data of all the genes were listed for one sample, then the count data for all the genes for the next sample, and so on.
This data format was highly inconvenient for later analyses so the data were reformatted into a ``gene by sample'' matrix format using the \textit{dplyr} package in \gls{r}.

Another problem with the data was the sample ID in the \gls{rnaseq} data.
Though similar to the \gls{tcga} sample IDs, the \gls{icgc} IDs in the \gls{rnaseq} data had an extra identification code in the sample names.
To associate each sample in the raw \gls{rnaseq} data from the \gls{icgc} database with the correct samples in the clinical data from the \gls{tcga} database, the \gls{icgc} IDs were re-coded to match the \gls{tcga} IDs.
After the IDs were re-coded, samples were checked to see if there were any duplicates in either the \gls{icgc} \gls{rnaseq} data or the \gls{tcga} clinical data.
Where there was a duplicate in the sample ID, a single sample with the highest mean expression value was chosen to represent that particular ID by using the \texttt{collapseRows} function in the \textit{WGCNA} package in \gls{r} \citep{Langfelder2008}.

@@

\begin{table}[htpb]
	\caption{Summary of the patient \gls{bmi} status in the \gls{icgc} cancer data}
	\label{tab:icgc_bmi}
	\begin{center}
		\begin{tabular}{lcccc}
			& \multicolumn{4}{c}{Number of samples}\\
			\cmidrule(r){2-5}
			Cancer type & Normal weight & Overweight & Obese & Total\\
			\hline
			\hline
			\rule{0pt}{2.25ex}BLCA & 103 & 97  & 61  & 261 \\
			CESC                   & 83  & 64  & 77  & 224 \\
			COAD                   & 75  & 81  & 70  & 226 \\
			KIRP                   & 26  & 53  & 45  & 124 \\
			LIHC                   & 139 & 76  & 49  & 264 \\
			READ                   & 22  & 36  & 15  & 73  \\
			SKCM                   & 71  & 74  & 73  & 218 \\
			UCEC                   & 88  & 108 & 286 & 482 \\
			\hline
			\hline
		\end{tabular}
	\end{center}
\end{table}

@@

\gls{kegg} is a genomic database constructed by \citet{Kanehisa2000} that store information about genes, pathways and ligands for a variety of species.
The \gls{kegg} database also curates other information such as the approved drugs in US and Japan and genes related to diseases, making it a great tool for exploring the biological significance of genes and pathways \citep{Kanehisa2008}.
The \textit{KEGG.db} package was used to load the \gls{kegg} database into \gls{r} \citep{kegg}.
Only the human related \gls{kegg} terms were used in pathway enrichment analysis, and these terms were organised into a format so that the pathways were able to be queried using the gene symbol.

@@

The Reactome database is a ``curated, peer-reviewed resource of human biological processes'' \citep{Joshi2005}.
The Reactome database is constructed based on the reactions that have direct evidence from the literature, which are connected into higher order pathway structures \citep{Joshi2005}.
The \textit{reactome.db} package was used to load the Reactome database into \gls{r} \citep{reactome}.
Only the human related Reactome terms were used in pathway enrichment analysis, and these terms were organised into a format so that the pathways were able to be queried using the gene symbol.

@@

Since the \gls{nzbc} data was the only data set (other than the Creighton \textit{et al.} data set) that had the patient \gls{bmi} information, all of the linear models were constructed in the \gls{nzbc} data set.
Eleven linear models were created in the \gls{nzbc} to predict the obesity associated metagene from the \citet{Creighton2012} study.
First seven models created were combinations of the sample \gls{bmi}, \gls{bmi} status and a selection of pathway associated metagene scores.
The selected pathways used in the linear model construction were \gls{bcat}, \gls{er}, \gls{ifna}, \gls{ifny}, Myc and \gls{pr}.
In deciding on the pathways to be used for the construction of the linear model, the correlation of the \gls{svd}- and transformation matrix-derived pathway metagene scores in different data sets were examined.

### 2017-03-29 thesis/misc/abstract.tex
tmp commit

Obesity has been a major global problem for more than a decade, associated with many noncommunicable diseases such as  cancer.
The number of obese people, in both adults and children, has risen in every country of the world and the trend will likely to continue in the future.
Cancers are caused by dysregulation of various molecular pathways that allow tumour cells to proliferate, survive and migrate.
One of the difficulties associated with the treatment of cancers is the identification of the underlying biological pathways that drive tumorigenesis.
This research aims to determine whether gene expression signatures exist  that are specific to obesity across multiple cancer types, and to investigate whether there are any common pathways being dysregulated in cancers based on these genetic signatures.
There were no genetic signatures or genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
However, the Akt, \gls{egfr} and Src pathways may have a role in promoting the tumour progression in patients that are obese.
It is likely that there is some complex mechanism underlying the relationship between obesity and cancer.
Better understanding of the pathways being dysregulated in cancer cells in obese patients may lead to improved clinical decisions, and contribute towards personalised treatment in the future.

>>>>

Obesity has been a major global problem for more than a decade, associated with many noncommunicable diseases such as  cancer.
The number of obese people, in both adults and children, has risen in every country of the world and the trend will likely to continue in the future.
Cancers are caused by dysregulation of various molecular pathways that allow tumour cells to proliferate, survive and migrate.
One of the difficulties associated with the treatment of cancers is the identification of the underlying biological pathways that drive tumorigenesis.
This research aims to determine whether gene expression signatures exist  that are specific to obesity across multiple cancer types, and to investigate whether there are any common pathways being dysregulated in cancers based on these genetic signatures.
There were no genetic signatures or genes differentially expressed between obese and non-obese patients that were common across multiple cancer types.
However, the Akt, \gls{egfr} and Src pathways may have a role in promoting the tumour progression in patients that are obese.
It is likely that there is some complex mechanism underlying the relationship between obesity and cancer.
A better understanding of the pathways being dysregulated in cancer cells in obese patients may lead to improved clinical decisions, and contribute towards personalised treatment in the future.

### 2017-03-29 thesis/misc/acknowledgement.tex
tmp commit

@@

First and foremost, I would like to thank my supervisor Mik, for giving me this project and an
opportunity to learn and develop the basic bioinformatics skills required to complete it.
You have been a great supervisor and I have learnt a lot from you over the past two years, and I have enjoyed being a part of the Black lab.
\\

@@

\noindent
I would also like to thank both past and present members of the Black lab, for useful tips and tricks to get me through my Masters.
Especially James Boocock, for introducing me to a variety of useful tool sets (by the way, everyone should start using vim); Murray Cadzow, for organising the fortnightly ``Sh*t You Should Know About'' sessions to learn more about R and other useful tools; and Tom Kelly, for being my companion in the Fish-bowl and helping me with some of the codes in my project.
\\

\noindent
I would like to thank all of my friends and family for all their support and fun memories throughout the years that I have been at the University.
Lastly, a special thanks to Gezza and Tessa who have generously agreed to proof-read my introduction.
\\

>>>>

\vspace*{\fill}

@@

First and foremost, I would like to thank my supervisor Mik, for giving me this project and an
opportunity to learn and develop the bioinformatics skills required to complete it.
You have been a great supervisor and I have learnt a lot from you over the past two years, and I have enjoyed being a part of the Black lab.
\\

@@

\noindent
I would also like to thank both past and present members of the Black lab, for useful tips and tricks to get me through my Masters.
Especially James Boocock, for introducing me to a variety of useful tool sets (by the way, everyone should start using vim); Murray Cadzow, for organising the fortnightly ``Shit You Should Know About'' (a.k.a. SYSKA) sessions to teach us more about R and other useful tools; and Tom Kelly, for being my companion in the Fish-bowl and helping me out with some of the codes in my project.
\\

\noindent
I would like to thank all of my friends and family, for all their support and fun memories throughout the years that I have been at University.
I wish I could name everyone, but I do not think it is a good idea to extend this thesis any longer\ldots
Long story short, my life would not be nearly as interesting or enjoyable without you guys.
\\

\noindent
Lastly, a special thanks to Gezza and Tessa who generously proof-read my introduction.
\\

\vfill

### 2017-03-29 thesis/misc/appendix.tex
tmp commit

\begin{appendices}
	\crefalias{chapter}{appcha}
	\crefalias{section}{appsec}
	\renewcommand{\thesection}{\Alph{chapter}\arabic{section}}

@@

	\section{Remainder of the results of the other Creighton \textit{et al.} obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_cr_icgc_cancer_heatmap_results}

@@

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{kirp} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{kirp} cancer data}
	\label{tab:degmetakirp}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.1853                      & 0.2590  & 0.3387             & -0.005657  & 0.5798              \\
			Res     & 0.1063                      & 0.1825  & 0.2128             & -0.005037  & 0.5368              \\
			CrOl    & 0.2576                      & 0.1757  & 0.3162             & -0.005763  & 0.5879              \\
			ResOl   & 0.3120                      & 0.1738  & 0.3198             & -0.004513  & 0.5048              \\
			Ca      & 0.2431                      & 0.2142  & 0.3591             & -0.005582  & 0.5743              \\
			CaRes   & 0.2327                      & 0.2344  & 0.3738             & -0.006250  & 0.6279              \\
			CaOl    & 0.3426                      & 0.2775  & 0.4693             & -0.007333  & 0.77469             \\
			CaResOl & 0.2643                      & 0.1315  & 0.2410             & -0.001408  & 0.3649              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

@@

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{skcm} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{skcm} cancer data}
	\label{tab:degmetaskcm}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.7115                      & 0.3329  & 0.6264             & 0.002887   & 0.2033              \\
			Res     & 0.7604                      & 0.5408  & 0.6396             & -0.001725  & 0.4296              \\
			CrOl    & 0.4719                      & 0.1224  & 0.2913             & 0.01261    & 0.05347             \\
			ResOl   & 0.8640                      & 0.1668  & 0.3051             & 0.01541    & {\bfseries 0.0372}\tnote{1}  \\
			Ca      & 0.8792                      & 0.2084  & 0.3739             & 0.006674   & 0.1184              \\
			CaRes   & 0.8098                      & 0.1950  & 0.3677             & 0.005746   & 0.1347              \\
			CaOl    & 0.9478                      & 0.2726  & 0.4471             & 0.01009    & 0.07449             \\
			CaResOl & 0.7309                      & 0.2561  & 0.2830             & 0.01606    & {\bfseries 0.03421} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
		\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{ucec} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{ucec} cancer data}
	\label{tab:degmetaucec}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.8357                      & 0.08117 & 0.1039             & 0.006952   & {\bfseries 0.03716}\tnote{1}\\
			Res     & 0.8664                      & 0.2023  & 0.3131             & 0.001998   & 0.1619              \\
			CrOl    & 0.9251                      & 0.3800  & 0.5800             & -0.000311  & 0.3569              \\
			ResOl   & 0.5826                      & 0.09608 & 0.2156             & 0.003487   & 0.1021              \\
			Ca      & 0.7491                      & 0.1103  & 0.1905             & 0.003811   & 0.09260             \\
			CaRes   & 0.8086                      & 0.2002  & 0.3419             & 0.0005824  & 0.2584              \\
			CaOl    & 0.9068                      & 0.2672  & 0.4153             & 0.00305    & 0.1166              \\
			CaResOl & 0.8360                      & 0.2440  & 0.4034             & 0.00022898 & 0.2863              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
		\item [1] All values in bold are statistically significant (p \textless{} 0.05).
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched \gls{kegg} pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_kegg}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type                      & Pathway         \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & NA\tnote{1}             \\
				\gls{cesc}                   & ABC transporter \\
				\gls{coad}                   & NA              \\
				\gls{kirp}                   & NA              \\
				\gls{lihc}                   & NA              \\
				\gls{read}                   & NA              \\
				\gls{skcm}                   & NA              \\
				\gls{ucec}                   & NA              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] Not available (no pathway enriched)
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched Reactome pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_reactome}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type & Pathway \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & Phosphate bond hydrolysis by NUDT proteins \\
				\gls{cesc}                   & Mitochondrial ABC transporters             \\
				\gls{coad}   & NA\tnote{1}               \\
				\gls{kirp}   & NA             \\
				\gls{lihc}   & NA             \\
				\gls{read}   & NA             \\
				\gls{skcm}   & NA             \\
				\gls{ucec}   & NA             \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] Not available (no pathway enriched)
		\end{tablenotes}
	\end{threeparttable}
\end{table}

>>>>

\begin{appendices}
	\crefalias{chapter}{appcha}
	\crefalias{section}{appsec}
	\renewcommand{\thesection}{\Alph{chapter}\arabic{section}}
	\renewcommand{\thetable}{S\arabic{table}}
	\renewcommand{\thefigure}{S\arabic{figure}}
	\setcounter{figure}{0}
	\setcounter{table}{0}

@@

	\section{Remainder of the results of the other CR obesity metagenes in the \gls{icgc} cancer data sets}
	\label{sec:rest_of_the_cr_icgc_cancer_heatmap_results}

@@

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{kirp} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{kirp} cancer data}
	\label{tab:degmetakirp}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.1853                      & 0.2590  & 0.3387             & -0.005657  & 0.5798              \\
			Res     & 0.1063                      & 0.1825  & 0.2128             & -0.005037  & 0.5368              \\
			CrOl    & 0.2576                      & 0.1757  & 0.3162             & -0.005763  & 0.5879              \\
			ResOl   & 0.3120                      & 0.1738  & 0.3198             & -0.004513  & 0.5048              \\
			Ca      & 0.2431                      & 0.2142  & 0.3591             & -0.005582  & 0.5743              \\
			CaRes   & 0.2327                      & 0.2344  & 0.3738             & -0.006250  & 0.6279              \\
			CaOl    & 0.3426                      & 0.2775  & 0.4693             & -0.007333  & 0.7747             \\
			CaResOl & 0.2643                      & 0.1315  & 0.2410             & -0.001408  & 0.3649              \\
			\hline
			\hline
		\end{tabular}
	\end{threeparttable}
\end{table}

@@

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{skcm} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{skcm} cancer data}
	\label{tab:degmetaskcm}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.7115                      & 0.3329  & 0.6264             & 0.002887   & 0.2033              \\
			Res     & 0.7604                      & 0.5408  & 0.6396             & -0.001725  & 0.4296              \\
			CrOl    & 0.4719                      & 0.1224  & 0.2913             & 0.01261    & 0.05347             \\
			ResOl   & 0.8640                      & 0.1668  & 0.3051             & 0.01541    & {\bfseries 0.0372}\tnote{1}  \\
			Ca      & 0.8792                      & 0.2084  & 0.3739             & 0.006674   & 0.1184              \\
			CaRes   & 0.8098                      & 0.1950  & 0.3677             & 0.005746   & 0.1347              \\
			CaOl    & 0.9478                      & 0.2726  & 0.4471             & 0.01009    & 0.07449             \\
			CaResOl & 0.7309                      & 0.2561  & 0.2830             & 0.01606    & {\bfseries 0.03421} \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption[Statistics of all the obesity metagenes in the \gls{icgc} \acrshort{ucec} cancer data]{Statistics of all the obesity metagenes in the \gls{icgc} \gls{ucec} cancer data}
	\label{tab:degmetaucec}
	\begin{threeparttable}
		\begin{tabular}{lccccc}
			& \multicolumn{3}{c}{ P-values} & \multicolumn{2}{c}{ Regression line statistics}\\
			\cmidrule(r){2-4} \cmidrule(r){5-6}
			Metagenes &  Overweight &  Obese &  \gls{anova} &  R$^2$ &  P \\
			\hline
			\hline
			\rule{0pt}{2.25ex}Cr      & 0.8357                      & 0.08117 & 0.1039             & 0.006952   & {\bfseries 0.03716}\tnote{1}\\
			Res     & 0.8664                      & 0.2023  & 0.3131             & 0.001998   & 0.1619              \\
			CrOl    & 0.9251                      & 0.3800  & 0.5800             & -0.000311  & 0.3569              \\
			ResOl   & 0.5826                      & 0.09608 & 0.2156             & 0.003487   & 0.1021              \\
			Ca      & 0.7491                      & 0.1103  & 0.1905             & 0.003811   & 0.09260             \\
			CaRes   & 0.8086                      & 0.2002  & 0.3419             & 0.0005824  & 0.2584              \\
			CaOl    & 0.9068                      & 0.2672  & 0.4153             & 0.00305    & 0.1166              \\
			CaResOl & 0.8360                      & 0.2440  & 0.4034             & 0.00022898 & 0.2863              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
				\item [1] All values in bold are statistically significant (p \textless{} 0.05).
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

@@

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched \gls{kegg} pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_kegg}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type                      & Pathway         \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & NA\tnote{1}             \\
				\gls{cesc}                   & ABC transporter \\
				\gls{coad}                   & NA              \\
				\gls{kirp}                   & NA              \\
				\gls{lihc}                   & NA              \\
				\gls{read}                   & NA              \\
				\gls{skcm}                   & NA              \\
				\gls{ucec}                   & NA              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
				\item [1] Not available (no pathway enriched)
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched Reactome pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_reactome}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type & Pathway \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & Phosphate bond hydrolysis by NUDT proteins \\
				\gls{cesc}                   & Mitochondrial ABC transporters             \\
				\gls{coad}   & NA\tnote{1}               \\
				\gls{kirp}   & NA             \\
				\gls{lihc}   & NA             \\
				\gls{read}   & NA             \\
				\gls{skcm}   & NA             \\
				\gls{ucec}   & NA             \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\begin{footnotesize}
				\item [1] Not available (no pathway enriched)
			\end{footnotesize}
		\end{tablenotes}
	\end{threeparttable}
\end{table}

### 2017-03-29 thesis/misc/appendix2.tex
tmp commit

	\section{Original result from \citet{Gatza2010a} study}
	\label{sec:result_from_gatza2010a_study}

@@

	\section{Summary of the remainder of the \gls{pr}-only linear models in \gls{nzbc} data}
	\label{sec:summary_of_the_pr_linear_models_in_nzbc_data}

@@

	\section{Summary statistics of the predicted obesity metagenes with sample \gls{bmi}/\gls{bmi} status in \gls{nzbc} and CR data}
	\label{sec:summary_statistics_of_the_predicted_obesity_metagenes_with_sample_bmi_bmi_status_in_nzbc_and_cr_data}

@@

>>>>

	\section{Original result from the \citet{Gatza2010a} study}
	\label{sec:result_from_gatza2010a_study}

@@

	\section{Summary of the remainder of the \gls{pr} linear models in \gls{nzbc} data}
	\label{sec:summary_of_the_pr_linear_models_in_nzbc_data}

@@

	\section{Summary statistics of the predicted obesity metagenes with sample \gls{bmi}/\gls{bmi} status in the \gls{nzbc} and CR data}
	\label{sec:summary_statistics_of_the_predicted_obesity_metagenes_with_sample_bmi_bmi_status_in_nzbc_and_cr_data}

@@

	\section{Code used in this project}
	\label{sec:code_used_in_this_project}

	All of the \gls{r} source code used in this project is publicly available at \url{https://github.com/rikutakei/bmi-cancer-code.git}.
	This thesis was written with \LaTeX{}, and the source code is publicly available at \url{https://github.com/rikutakei/mastersDoc.git}.
